% !TEX root = main.tex
The AUP can be found at \hfill \\ \url{http://www.rug.nl/science-and-society/centre-for-information-technology/security/aup/}.
\begin{itemize}
	\item System managers have more responsibilities than normal users. The do have more privileges. They have the privilege to install software.
	\item ``Als uitgangspunt geldt dan ook dezelfde grondregel die ook in het verkeer geldt: de gebruiker van de Universitaire Computer Systemen mag deze systemen niet in gevaar brengen of andere gebruikers hinderen.''
	\item \begin{enumerate}
		\item Users should keep their account information private.
		\item Users should report security holes.
		\item Users should not use the system for commercial use.
		\item Users should not copy software from the system.
		\end{enumerate}
	\item \begin{enumerate}
		\item It is forbidden to modify or remove hardware and/or software without prior permission from proper authorities.
		\item It is forbidden to harass or hinder other users of the university computer systems.
		\item It is forbidden to gain access to, or to distribute any information stored in the university computer systems without having obtained prior permission of the owner of such software or data.
		\item It is forbidden to distribute or to make available any information, irrespective of its form, owned by the university, without having obtained written permission by the owner in advance.
		\end{enumerate}
	\item The user's privileges will either be suspended or restricted during the investigation. Data carriers of the suspect will also be inspected. The board of the suspect's faculty or the director of their department will also be informed.
	\item The suspect may go to the chair of his/her department and file a complaint there.
\end{itemize}